---
title: "Normality"
author: "Sarah Green"
format: html
embed-resources: true
editor: visual
---

```{r}
#| echo: false
#| warning: false

library(readr)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(rstatix)
library(tidyr)
library(kableExtra)


df <- read_csv("FILTERED DATA.csv") %>%
  mutate(OUTCOME = case_when(
    (RESULT == "HIT" | RESULT == "GOAL" | RESULT == "BEHIND" | RESULT == "NO SCORE") ~ 'EFFECTIVE',
    (RESULT == "NEUTRAL" | (RESULT == "NO DISPOSAL" & lead(TEAM_BALL == "STOPPAGE", 1)) | (RESULT == "NO DISPOSAL" & lead(TEAM_BALL == "OFFENCE WIN", 1))) ~ 'NEUTRAL',
    (RESULT == "MISS" | (RESULT == "NO DISPOSAL" & lead(TEAM_BALL == "DEFENCE WIN", 1))) ~ 'INEFFECTIVE'
  ))

df.week <- df %>%
  dplyr::group_by(WEEK, SETTING) %>%
  summarise(
    # TEAM WON BALL
    OFF_WIN = sum(TEAM_BALL == "OFFENCE WIN", na.rm = T), 
    DEF_WIN = sum(TEAM_BALL == "DEFENCE WIN", na.rm = T), 
    STOPPAGE = sum(TEAM_BALL == "STOPPAGE", na.rm = T),
    #POSS TYPE
    MARK = sum(GAIN_POSS == "MARK", na.rm = T), 
    GP = sum(GAIN_POSS == "GP", na.rm = T), 
    GB = sum(GAIN_POSS == "GROUNDBALL-GET", na.rm = T), 
    #DISPOAL TYPE
    KICK = sum(DISPOSAL == "KICK", na.rm = T), 
    HB = sum(DISPOSAL == "HANDBALL", na.rm = T), 
    TACKLED = sum(DISPOSAL == "TACKLED", na.rm = T),
    #TIP
    DURATION_0_1S= sum(DURATION <=1, na.rm = T), 
    DURATION_1_2S = sum(DURATION >1 & DURATION <=2, na.rm = T), 
    DURATION_2_3S = sum(DURATION >2 & DURATION <=3, na.rm = T), 
    DURATION_MORE3S = sum(DURATION >3, na.rm = T), 
    #MOVEMENT
    DYNAMIC = sum(MOVEMENT == "DYNAMIC", na.rm = T), 
    STATIONARY = sum(MOVEMENT == "STATIONARY", na.rm = T), 
    #PRESSURE
    PHYSICAL = sum(PRESSURE == "PHYSICAL", na.rm = T), 
    CLOSING = sum(PRESSURE == "CLOSING", na.rm = T), 
    CHASING = sum(PRESSURE == "CHASING", na.rm = T), 
    CORRALLING = sum(PRESSURE == "CORRALLING", na.rm = T), 
    SET = sum(PRESSURE == "SET PRESSURE", na.rm = T), 
    NO_PRESSURE = sum(PRESSURE == "NO PRESSURE", na.rm = T), 
    #CARRIER DENSITY
    MORE3_OPP = sum(CARRIER_DENSITY == "MORE 3 OPPO", na.rm = T), 
    THREE_OPPO = sum(CARRIER_DENSITY == "3 OPPO", na.rm = T), 
    TWO_OPPO = sum(CARRIER_DENSITY == "2 OPPO", na.rm = T), 
    ONE_OPPO = sum(CARRIER_DENSITY == "1 OPPO", na.rm = T), 
    NO_OPPO = sum(CARRIER_DENSITY == "NO OPP", na.rm = T), 
    #DISTANCE
    SHORT_DIST = sum(DISTANCE == "0-25M", na.rm = T), 
    MEDIUM_DIST = sum(DISTANCE == "25-40M", na.rm = T), 
    LONG_DIST = sum(DISTANCE == "40+", na.rm = T), 
    DIST_NO = sum(DISTANCE == "NO DISPOSAL", na.rm = T),
    #RECEIVER DENSITY
    UNCONTESTED = sum(RECEIVER_DENSITY == "UNCONTESTED", na.rm = T),
    EVEN = sum((RECEIVER_DENSITY == "EVEN") | (RECEIVER_DENSITY == "CONTEST"), na.rm = T),
    SUPERIOR = sum(RECEIVER_DENSITY == "SUPERIOR", na.rm = T),
    INFERIOR = sum(RECEIVER_DENSITY == "INFERIOR", na.rm = T),
    LEADING = sum(RECEIVER_DENSITY == "LEADING", na.rm = T),
    SHOT_GOAL = sum(RECEIVER_DENSITY == "SHOT AT GOAL", na.rm = T),
    NO_RECIEVER = sum(RECEIVER_DENSITY == "NO RECEIVER", na.rm = T),
    RECIEVE_NO = sum(RECEIVER_DENSITY == "NO DISPOSAL", na.rm = T),
    #OUTCOME
    EFFECTIVE = sum(OUTCOME == "EFFECTIVE", na.rm = T),
    INEFFECTIVE = sum(OUTCOME == "INEFFECTIVE", na.rm = T),
    NEUTRAL = sum(OUTCOME == "NEUTRAL", na.rm = T)
    
  ) %>%
  distinct() %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  pivot_longer(!c(SETTING, WEEK), names_to = "VARIABLE",  values_to = "VALUE")
  


```

## 1. TRAINING

```{r}
#| echo: false
#| warning: false

df.training <- df.week[-23,] %>%
  filter(SETTING == "TRAINING") 
```

1a) Shapiro wilk

Team Won Ball: p\<0.05 (sig)

```{r}
#| echo: false
#| warning: false

teamwonball_shap <- df.training %>%
  filter(VARIABLE %in% c("OFF_WIN", "DEF_WIN", "STOPPAGE")) %>%
  ungroup() %>%
  shapiro_test(VALUE)
  
teamwonball_shap %>% 
  kbl(caption = "Shapiro-Wilk Test - Team Won Ball",
      col.names = c("Variable", "Statistic", "p-value")) %>%
  kable_classic_2(full_width = FALSE)

teamwonball_plot <- df.training %>%
  filter(VARIABLE %in% c("OFF_WIN", "DEF_WIN", "STOPPAGE"))
  
ggplot(teamwonball_plot, aes(x= VARIABLE, y = VALUE)) +
  geom_violin(scale = "count", aes(fill = VARIABLE)) +
  geom_boxplot(width = 0.02) +
  theme(legend.position = "none")

```

Gain possession p\<0.05 (sig)

```{r}
#| echo: false
#| warning: false

gainposs_shap <- df.training %>%
  filter(VARIABLE %in% c("MARK", "GP", "GB")) %>%
  ungroup() %>%
  shapiro_test(VALUE)
  
gainposs_shap %>% 
  kbl(caption = "Shapiro-Wilk Test - Gained Possession",
      col.names = c("Variable", "Statistic", "p-value")) %>%
  kable_classic_2(full_width = FALSE)

gainposs_plot <- df.training %>%
    filter(VARIABLE %in% c("MARK", "GP", "GB"))

ggplot(gainposs_plot, aes(x= VARIABLE, y = VALUE)) +
  geom_violin(scale = "count", aes(fill = VARIABLE)) +
  geom_boxplot(width = 0.05) +
  theme(legend.position = "none")

```

Disposal p\<0.05 (sig)

```{r}
#| echo: false
#| warning: false

disposal_shap <- df.training %>%
  filter(VARIABLE %in% c("KICK", "HB", "TACKLED")) %>%
  ungroup() %>%
  shapiro_test(VALUE)
  
disposal_shap %>% 
  kbl(caption = "Shapiro-Wilk Test - Disposal Type",
      col.names = c("Variable", "Statistic", "p-value")) %>%
  kable_classic_2(full_width = FALSE)

disposal_plot <- df.training %>%
      filter(VARIABLE %in% c("KICK", "HB", "TACKLED"))

ggplot(disposal_plot, aes(x= VARIABLE, y = VALUE)) +
  geom_violin(scale = "count", aes(fill = VARIABLE)) +
  geom_boxplot(width = 0.03) +
  theme(legend.position = "none")
```

Duration p\<0.05 (sig)

```{r}
#| echo: false
#| warning: false

duration_shap <- df.training %>%
  filter(VARIABLE %in% c("DURATION_0_1S", "DURATION_1_2S", "DURATION_2_3S", "DURATION_MORE3S")) %>%
  ungroup() %>%
  shapiro_test(VALUE)
  
duration_shap %>% 
  kbl(caption = "Shapiro-Wilk Test - Disposal Duration",
      col.names = c("Variable", "Statistic", "p-value")) %>%
  kable_classic_2(full_width = FALSE)


duration_plot <- df.training %>%
  filter(VARIABLE %in% c("DURATION_0_1S", "DURATION_1_2S", "DURATION_2_3S", "DURATION_MORE3S"))

ggplot(duration_plot, aes(x= VARIABLE, y = VALUE)) +
  geom_violin(scale = "count", aes(fill = VARIABLE)) +
  geom_boxplot(width = 0.03) +
  theme(legend.position = "none")
```

Movement p\>0.05 (non-sig)

```{r}
#| echo: false
#| warning: false

movement_shap <- df.training %>%
  filter(VARIABLE %in% c("DYNAMIC", "STATIONARY")) %>%
  ungroup() %>%
  shapiro_test(VALUE)
  
movement_shap %>% 
  kbl(caption = "Shapiro-Wilk Test - Disposal Movement",
      col.names = c("Variable", "Statistic", "p-value")) %>%
  kable_classic_2(full_width = FALSE)

movement_plot <- df.training %>%
    filter(VARIABLE %in% c("DYNAMIC", "STATIONARY"))

ggplot(movement_plot, aes(x= VARIABLE, y = VALUE)) +
  geom_violin(scale = "count", aes(fill = VARIABLE)) +
  geom_boxplot(width = 0.05) +
  theme(legend.position = "none")
```

Pressure p\<0.05 (sig)

```{r}
#| echo: false
#| warning: false

pressure_shap <- df.training %>%
  filter(VARIABLE %in% c("PHYSICAL", "CLOSING", "CHASING", "CORRALLING", "SET", "NO_PRESSURE")) %>%
  ungroup() %>%
  shapiro_test(VALUE)
  
pressure_shap %>% 
  kbl(caption = "Shapiro-Wilk Test - Pressure",
      col.names = c("Variable", "Statistic", "p-value")) %>%
  kable_classic_2(full_width = FALSE)


pressure_plot <- df.training %>%
    filter(VARIABLE %in% c("PHYSICAL", "CLOSING", "CHASING", "CORRALLING", "SET", "NO_PRESSURE"))

ggplot(pressure_plot, aes(x= VARIABLE, y = VALUE)) +
  geom_violin(scale = "count", aes(fill = VARIABLE)) +
  geom_boxplot(width = 0.02) +
  theme(legend.position = "none")
```

Carrier density p\<0.05 (sig)

```{r}
#| echo: false
#| warning: false

density_shap <- df.training %>%
  filter(VARIABLE %in% c("NO_OPPO", "ONE_OPPO", "TWO_OPPO", "THREE_OPPO", "MORE3_OPP")) %>%
  ungroup() %>%
  shapiro_test(VALUE)
  
density_shap %>% 
  kbl(caption = "Shapiro-Wilk Test - Carrier Density",
      col.names = c("Variable", "Statistic", "p-value")) %>%
  kable_classic_2(full_width = FALSE)

density_plot <- df.training %>%
    filter(VARIABLE %in% c("NO_OPPO", "ONE_OPPO", "TWO_OPPO", "THREE_OPPO", "MORE3_OPP"))

ggplot(density_plot, aes(x= VARIABLE, y = VALUE)) +
  geom_violin(scale = "count", aes(fill = VARIABLE)) +
  geom_boxplot(width = 0.04) +
  theme(legend.position = "none")
```

Distance p\<0.05 (sig)

```{r}
#| echo: false
#| warning: false

distance_shap <- df.training %>%
  filter(VARIABLE %in% c("DIST_NO", "SHORT_DIST", "MEDIUM_DIST", "LONG_DIST")) %>%
  ungroup() %>%
  shapiro_test(VALUE)
  
distance_shap %>% 
  kbl(caption = "Shapiro-Wilk Test - Distance",
      col.names = c("Variable", "Statistic", "p-value")) %>%
  kable_classic_2(full_width = FALSE)

distance_plot <- df.training %>%
    filter(VARIABLE %in% c("DIST_NO", "SHORT_DIST", "MEDIUM_DIST", "LONG_DIST"))

ggplot(distance_plot, aes(x= VARIABLE, y = VALUE)) +
  geom_violin(scale = "count", aes(fill = VARIABLE)) +
  geom_boxplot(width = 0.03) +
  theme(legend.position = "none")
```

Receiver density p\<0.05 (sig)

```{r}
#| echo: false
#| warning: false

reciever_shap <- df.training %>%
  filter(VARIABLE %in% c("EVEN", "SUPERIOR", "INFERIOR", "LEADING", "UNCONTESTED", "SHOT_GOAL", "RECIEVE_NO")) %>%
  ungroup() %>%
  shapiro_test(VALUE)
  
reciever_shap %>% 
  kbl(caption = "Shapiro-Wilk Test - Receiever Density",
      col.names = c("Variable", "Statistic", "p-value")) %>%
  kable_classic_2(full_width = FALSE)

reciever_plot <- df.training %>%
    filter(VARIABLE %in% c("EVEN", "SUPERIOR", "INFERIOR", "LEADING", "UNCONTESTED", "SHOT_GOAL", "RECIEVE_NO"))

ggplot(reciever_plot, aes(x= VARIABLE, y = VALUE)) +
  geom_violin(scale = "count", aes(fill = VARIABLE)) +
  geom_boxplot(width = 0.02) +
  theme(legend.position = "none")
```

Outcome p\<0.05 (sig)

```{r}
#| echo: false
#| warning: false

result_shap <- df.training %>%
  filter(VARIABLE %in% c("EFFECTIVE", "INEFFECTIVE", "NEUTRAL")) %>%
  ungroup() %>%
  shapiro_test(VALUE)
  
result_shap %>% 
  kbl(caption = "Shapiro-Wilk Test - Disposal Outcome",
      col.names = c("Variable", "Statistic", "p-value")) %>%
  kable_classic_2(full_width = FALSE)

result_plot <- df.training %>%
    filter(VARIABLE %in% c("EFFECTIVE", "INEFFECTIVE", "NEUTRAL"))

ggplot(result_plot, aes(x= VARIABLE, y = VALUE)) +
  geom_violin(scale = "count", aes(fill = VARIABLE)) +
  geom_boxplot(width = 0.02) +
  theme(legend.position = "none")
```

## 2. MATCH

```{r}
#| echo: false
#| warning: false

df.match <- df.week[-23,] %>%
  filter(SETTING == "MATCH")

```

Team Won Ball: p\<0.05 (sig)

```{r}
#| echo: false
#| warning: false

teamwonball_shap <- df.match %>%
  filter(VARIABLE %in% c("OFF_WIN", "DEF_WIN", "STOPPAGE")) %>%
  ungroup() %>%
  shapiro_test(VALUE)
  
teamwonball_shap %>% 
  kbl(caption = "Shapiro-Wilk Test - Team Won Ball",
      col.names = c("Variable", "Statistic", "p-value")) %>%
  kable_classic_2(full_width = FALSE)

teamwonball_plot <- df.match %>%
  filter(VARIABLE %in% c("OFF_WIN", "DEF_WIN", "STOPPAGE"))
  
ggplot(teamwonball_plot, aes(x= VARIABLE, y = VALUE)) +
  geom_violin(scale = "count", aes(fill = VARIABLE)) +
  geom_boxplot(width = 0.01) +
  theme(legend.position = "none")

```

Gain possession p\<0.05 (sig)

```{r}
#| echo: false
#| warning: false

gainposs_shap <- df.match %>%
  filter(VARIABLE %in% c("MARK", "GP", "GB")) %>%
  ungroup() %>%
  shapiro_test(VALUE)
  
gainposs_shap %>% 
  kbl(caption = "Shapiro-Wilk Test - Gained Possession",
      col.names = c("Variable", "Statistic", "p-value")) %>%
  kable_classic_2(full_width = FALSE)

gainposs_plot <- df.match %>%
    filter(VARIABLE %in% c("MARK", "GP", "GB"))

ggplot(gainposs_plot, aes(x= VARIABLE, y = VALUE)) +
  geom_violin(scale = "count", aes(fill = VARIABLE)) +
  geom_boxplot(width = 0.05) +
  theme(legend.position = "none")

```

Disposal p\<0.05 (sig)

```{r}
#| echo: false
#| warning: false

disposal_shap <- df.match %>%
  filter(VARIABLE %in% c("KICK", "HB", "TACKLED")) %>%
  ungroup() %>%
  shapiro_test(VALUE)
  
disposal_shap %>% 
  kbl(caption = "Shapiro-Wilk Test - Disposal Type",
      col.names = c("Variable", "Statistic", "p-value")) %>%
  kable_classic_2(full_width = FALSE)

disposal_plot <- df.match %>%
      filter(VARIABLE %in% c("KICK", "HB", "TACKLED"))

ggplot(disposal_plot, aes(x= VARIABLE, y = VALUE)) +
  geom_violin(scale = "count", aes(fill = VARIABLE)) +
  geom_boxplot(width = 0.03) +
  theme(legend.position = "none")
```

Duration p\<0.05 (sig)

```{r}
#| echo: false
#| warning: false

duration_shap <- df.match %>%
  filter(VARIABLE %in% c("DURATION_0_1S", "DURATION_1_2S", "DURATION_2_3S", "DURATION_MORE3S")) %>%
  ungroup() %>%
  shapiro_test(VALUE)
  
duration_shap %>% 
  kbl(caption = "Shapiro-Wilk Test - Disposal Duration",
      col.names = c("Variable", "Statistic", "p-value")) %>%
  kable_classic_2(full_width = FALSE)


duration_plot <- df.match %>%
  filter(VARIABLE %in% c("DURATION_0_1S", "DURATION_1_2S", "DURATION_2_3S", "DURATION_MORE3S"))

ggplot(duration_plot, aes(x= VARIABLE, y = VALUE)) +
  geom_violin(scale = "count", aes(fill = VARIABLE)) +
  geom_boxplot(width = 0.03) +
  theme(legend.position = "none")
```

Movement p\<0.05 (sig)

```{r}
#| echo: false
#| warning: false

movement_shap <- df.match %>%
  filter(VARIABLE %in% c("DYNAMIC", "STATIONARY")) %>%
  ungroup() %>%
  shapiro_test(VALUE)
  
movement_shap %>% 
  kbl(caption = "Shapiro-Wilk Test - Disposal Movement",
      col.names = c("Variable", "Statistic", "p-value")) %>%
  kable_classic_2(full_width = FALSE)

movement_plot <- df.match %>%
    filter(VARIABLE %in% c("DYNAMIC", "STATIONARY"))

ggplot(movement_plot, aes(x= VARIABLE, y = VALUE)) +
  geom_violin(scale = "count", aes(fill = VARIABLE)) +
  geom_boxplot(width = 0.05) +
  theme(legend.position = "none")
```

Pressure p\<0.05 (sig)

```{r}
#| echo: false
#| warning: false

pressure_shap <- df.match %>%
  filter(VARIABLE %in% c("PHYSICAL", "CLOSING", "CHASING", "CORRALLING", "SET", "NO_PRESSURE")) %>%
  ungroup() %>%
  shapiro_test(VALUE)
  
pressure_shap %>% 
  kbl(caption = "Shapiro-Wilk Test - Pressure",
      col.names = c("Variable", "Statistic", "p-value")) %>%
  kable_classic_2(full_width = FALSE)


pressure_plot <- df.match %>%
    filter(VARIABLE %in% c("PHYSICAL", "CLOSING", "CHASING", "CORRALLING", "SET", "NO_PRESSURE"))

ggplot(pressure_plot, aes(x= VARIABLE, y = VALUE)) +
  geom_violin(scale = "count", aes(fill = VARIABLE)) +
  geom_boxplot(width = 0.01) +
  theme(legend.position = "none")
```

Carrier density p\<0.05 (sig)

```{r}
#| echo: false
#| warning: false

density_shap <- df.match %>%
  filter(VARIABLE %in% c("NO_OPPO", "ONE_OPPO", "TWO_OPPO", "THREE_OPPO", "MORE3_OPP")) %>%
  ungroup() %>%
  shapiro_test(VALUE)
  
density_shap %>% 
  kbl(caption = "Shapiro-Wilk Test - Carrier Density",
      col.names = c("Variable", "Statistic", "p-value")) %>%
  kable_classic_2(full_width = FALSE)

density_plot <- df.match %>%
    filter(VARIABLE %in% c("NO_OPPO", "ONE_OPPO", "TWO_OPPO", "THREE_OPPO", "MORE3_OPP"))

ggplot(density_plot, aes(x= VARIABLE, y = VALUE)) +
  geom_violin(scale = "count", aes(fill = VARIABLE)) +
  geom_boxplot(width = 0.04) +
  theme(legend.position = "none")
```

Distance p\<0.05 (sig)

```{r}
#| echo: false
#| warning: false

distance_shap <- df.match %>%
  filter(VARIABLE %in% c("DIST_NO", "SHORT_DIST", "MEDIUM_DIST", "LONG_DIST")) %>%
  ungroup() %>%
  shapiro_test(VALUE)
  
distance_shap %>% 
  kbl(caption = "Shapiro-Wilk Test - Distance",
      col.names = c("Variable", "Statistic", "p-value")) %>%
  kable_classic_2(full_width = FALSE)

distance_plot <- df.match %>%
    filter(VARIABLE %in% c("DIST_NO", "SHORT_DIST", "MEDIUM_DIST", "LONG_DIST"))

ggplot(distance_plot, aes(x= VARIABLE, y = VALUE)) +
  geom_violin(scale = "count", aes(fill = VARIABLE)) +
  geom_boxplot(width = 0.03) +
  theme(legend.position = "none")
```

Receiver density p\<0.05 (sig)

```{r}
#| echo: false
#| warning: false

reciever_shap <- df.match %>%
  filter(VARIABLE %in% c("EVEN", "SUPERIOR", "INFERIOR", "LEADING", "UNCONTESTED", "SHOT_GOAL", "RECIEVE_NO")) %>%
  ungroup() %>%
  shapiro_test(VALUE)
  
reciever_shap %>% 
  kbl(caption = "Shapiro-Wilk Test - Receiever Density",
      col.names = c("Variable", "Statistic", "p-value")) %>%
  kable_classic_2(full_width = FALSE)

reciever_plot <- df.match %>%
    filter(VARIABLE %in% c("EVEN", "SUPERIOR", "INFERIOR", "LEADING", "UNCONTESTED", "SHOT_GOAL", "RECIEVE_NO"))

ggplot(reciever_plot, aes(x= VARIABLE, y = VALUE)) +
  geom_violin(scale = "count", aes(fill = VARIABLE)) +
  geom_boxplot(width = 0.02) +
  theme(legend.position = "none")
```

Outcome p\<0.05 (sig)

```{r}
#| echo: false
#| warning: false

result_shap <- df.match %>%
  filter(VARIABLE %in% c("EFFECTIVE", "INEFFECTIVE", "NEUTRAL")) %>%
  ungroup() %>%
  shapiro_test(VALUE)
  
result_shap %>% 
  kbl(caption = "Shapiro-Wilk Test - Disposal Outcome",
      col.names = c("Variable", "Statistic", "p-value")) %>%
  kable_classic_2(full_width = FALSE)

result_plot <- df.match %>%
    filter(VARIABLE %in% c("EFFECTIVE", "INEFFECTIVE", "NEUTRAL"))

ggplot(result_plot, aes(x= VARIABLE, y = VALUE)) +
  geom_violin(scale = "count", aes(fill = VARIABLE)) +
  geom_boxplot(width = 0.02) +
  theme(legend.position = "none")
```

I50 p\>0.05 (non-sig)

```{r}
#| echo: false
#| warning: false

i50_shap <- df.match %>%
  filter(VARIABLE == "I50") %>%
  ungroup() %>%
  shapiro_test(VALUE)
  
i50_shap %>% 
  kbl(caption = "Shapiro-Wilk Test - I50",
      col.names = c("Variable", "Statistic", "p-value")) %>%
  kable_classic_2(full_width = FALSE)

i50_plot <- df.match %>%
    filter(VARIABLE == "I50")

ggplot(i50_plot, aes(x= VARIABLE, y = VALUE)) +
  geom_violin(scale = "count", aes(fill = VARIABLE)) +
  geom_boxplot(width = 0.02) +
  theme(legend.position = "none")

```

Rebound 50

```{r}
#| echo: false
#| warning: false

rebound50_shap <- df.match %>%
  filter(VARIABLE == "REBOUND50") %>%
  ungroup() %>%
  shapiro_test(VALUE)
  
rebound50_shap %>% 
  kbl(caption = "Shapiro-Wilk Test - I50",
      col.names = c("Variable", "Statistic", "p-value")) %>%
  kable_classic_2(full_width = FALSE)

rebound50_plot <- df.match %>%
    filter(VARIABLE == "REBOUND50")

ggplot(rebound50_plot, aes(x= VARIABLE, y = VALUE)) +
  geom_violin(scale = "count", aes(fill = VARIABLE)) +
  geom_boxplot(width = 0.05) +
  theme(legend.position = "none")
```

### 3. SETTING COMBINED

```{r}
#| echo: false
#| warning: false

df.overall <- df.week[-23,]
```

Team Won Ball: p\<0.05 (sig)

```{r}
#| echo: false
#| warning: false

teamwonball_shap <- df.overall %>%
  filter(VARIABLE %in% c("OFF_WIN", "DEF_WIN", "COACH_FEED", "STOPPAGE")) %>%
  ungroup() %>%
  shapiro_test(VALUE)
  
teamwonball_shap %>% 
  kbl(caption = "Shapiro-Wilk Test - Team Won Ball",
      col.names = c("Variable", "Statistic", "p-value")) %>%
  kable_classic_2(full_width = FALSE)

teamwonball_plot <- df.overall %>%
  filter(VARIABLE %in% c("OFF_WIN", "DEF_WIN", "COACH_FEED", "STOPPAGE"))
  
ggplot(teamwonball_plot, aes(x= VARIABLE, y = VALUE)) +
  geom_violin(scale = "count", aes(fill = VARIABLE)) +
  geom_boxplot(width = 0.02) +
  theme(legend.position = "none")

```

Gain possession p\<0.05 (sig)

```{r}
#| echo: false
#| warning: false

gainposs_shap <- df.overall %>%
  filter(VARIABLE %in% c("MARK", "GP", "GB")) %>%
  ungroup() %>%
  shapiro_test(VALUE)
  
gainposs_shap %>% 
  kbl(caption = "Shapiro-Wilk Test - Gained Possession",
      col.names = c("Variable", "Statistic", "p-value")) %>%
  kable_classic_2(full_width = FALSE)

gainposs_plot <- df.overall %>%
    filter(VARIABLE %in% c("MARK", "GP", "GB"))

ggplot(gainposs_plot, aes(x= VARIABLE, y = VALUE)) +
  geom_violin(scale = "count", aes(fill = VARIABLE)) +
  geom_boxplot(width = 0.02) +
  theme(legend.position = "none")

```

Key moment p\<0.05 (sig)

```{r}
#| echo: false
#| warning: false

keymoment_shap <- df.overall %>%
  filter(VARIABLE %in% c("CLEARENCE", "POST_MARKING_CONTEST")) %>%
  ungroup() %>%
  shapiro_test(VALUE)
  
keymoment_shap %>% 
  kbl(caption = "Shapiro-Wilk Test - Key Moment",
      col.names = c("Variable", "Statistic", "p-value")) %>%
  kable_classic_2(full_width = FALSE)

keymoment_plot <- df.overall %>%
      filter(VARIABLE %in% c("CLEARENCE", "POST_MARKING_CONTEST"))

ggplot(keymoment_plot, aes(x= VARIABLE, y = VALUE)) +
  geom_violin(aes(fill = VARIABLE)) +
  geom_boxplot(width = 0.02) +
  theme(legend.position = "none")


```

Disposal p\<0.05 (sig)

```{r}
#| echo: false
#| warning: false

disposal_shap <- df.overall %>%
  filter(VARIABLE %in% c("KICK", "HB", "TACKLED")) %>%
  ungroup() %>%
  shapiro_test(VALUE)
  
disposal_shap %>% 
  kbl(caption = "Shapiro-Wilk Test - Disposal Type",
      col.names = c("Variable", "Statistic", "p-value")) %>%
  kable_classic_2(full_width = FALSE)

disposal_plot <- df.overall %>%
      filter(VARIABLE %in% c("KICK", "HB", "TACKLED"))

ggplot(disposal_plot, aes(x= VARIABLE, y = VALUE)) +
  geom_violin(scale = "count", aes(fill = VARIABLE)) +
  geom_boxplot(width = 0.03) +
  theme(legend.position = "none")
```

Duration p\<0.05 (sig)

```{r}
#| echo: false
#| warning: false

duration_shap <- df.overall %>%
  filter(VARIABLE %in% c("DURATION_0_1S", "DURATION_1_2S", "DURATION_2_3S", "DURATION_MORE3S")) %>%
  ungroup() %>%
  shapiro_test(VALUE)
  
duration_shap %>% 
  kbl(caption = "Shapiro-Wilk Test - Disposal Duration",
      col.names = c("Variable", "Statistic", "p-value")) %>%
  kable_classic_2(full_width = FALSE)


duration_plot <- df.overall %>%
  filter(VARIABLE %in% c("DURATION_0_1S", "DURATION_1_2S", "DURATION_2_3S", "DURATION_MORE3S"))

ggplot(duration_plot, aes(x= VARIABLE, y = VALUE)) +
  geom_violin(scale = "count", aes(fill = VARIABLE)) +
  geom_boxplot(width = 0.03) +
  theme(legend.position = "none")
```

Location p\<0.05 (sig)

```{r}
#| echo: false
#| warning: false

zone_shap <- df.overall %>%
  filter(VARIABLE %in% c("D50_START", "DEF_MID_ARC_START", "OFF_MID_ARC_START", "F50_START")) %>%
  ungroup() %>%
  shapiro_test(VALUE)
  
zone_shap %>% 
  kbl(caption = "Shapiro-Wilk Test - Disposal Location",
      col.names = c("Variable", "Statistic", "p-value")) %>%
  kable_classic_2(full_width = FALSE)

zone_plot <- df.overall %>%
  filter(VARIABLE %in% c("D50_START", "DEF_MID_ARC_START", "OFF_MID_ARC_START", "F50_START"))

ggplot(zone_plot, aes(x= VARIABLE, y = VALUE)) +
  geom_violin(scale = "count", aes(fill = VARIABLE)) +
  geom_boxplot(width = 0.05) +
  theme(legend.position = "none")
```

Movement p\<0.05 (sig)

```{r}
#| echo: false
#| warning: false

movement_shap <- df.overall %>%
  filter(VARIABLE %in% c("DYNAMIC", "STATIONARY")) %>%
  ungroup() %>%
  shapiro_test(VALUE)
  
movement_shap %>% 
  kbl(caption = "Shapiro-Wilk Test - Disposal Movement",
      col.names = c("Variable", "Statistic", "p-value")) %>%
  kable_classic_2(full_width = FALSE)

movement_plot <- df.overall %>%
    filter(VARIABLE %in% c("DYNAMIC", "STATIONARY"))

ggplot(movement_plot, aes(x= VARIABLE, y = VALUE)) +
  geom_violin(scale = "count", aes(fill = VARIABLE)) +
  geom_boxplot(width = 0.05) +
  theme(legend.position = "none")
```

Pressure p\<0.05 (sig)

```{r}
#| echo: false
#| warning: false

pressure_shap <- df.overall %>%
  filter(VARIABLE %in% c("PHYSICAL", "CLOSING", "CHASING", "CORRALLING", "SET", "NO_PRESSURE")) %>%
  ungroup() %>%
  shapiro_test(VALUE)
  
pressure_shap %>% 
  kbl(caption = "Shapiro-Wilk Test - Pressure",
      col.names = c("Variable", "Statistic", "p-value")) %>%
  kable_classic_2(full_width = FALSE)


pressure_plot <- df.overall %>%
    filter(VARIABLE %in% c("PHYSICAL", "CLOSING", "CHASING", "CORRALLING", "SET", "NO_PRESSURE"))

ggplot(pressure_plot, aes(x= VARIABLE, y = VALUE)) +
  geom_violin(scale = "count", aes(fill = VARIABLE)) +
  #geom_boxplot(width = 0.01) +
  theme(legend.position = "none")
```

Carrier density p\<0.05 (sig)

```{r}
#| echo: false
#| warning: false

density_shap <- df.overall %>%
  filter(VARIABLE %in% c("NO_OPPO", "ONE_OPPO", "TWO_OPPO", "THREE_OPPO", "MORE3_OPP")) %>%
  ungroup() %>%
  shapiro_test(VALUE)
  
density_shap %>% 
  kbl(caption = "Shapiro-Wilk Test - Carrier Density",
      col.names = c("Variable", "Statistic", "p-value")) %>%
  kable_classic_2(full_width = FALSE)

density_plot <- df.overall %>%
    filter(VARIABLE %in% c("NO_OPPO", "ONE_OPPO", "TWO_OPPO", "THREE_OPPO", "MORE3_OPP"))

ggplot(density_plot, aes(x= VARIABLE, y = VALUE)) +
  geom_violin(scale = "count", aes(fill = VARIABLE)) +
  geom_boxplot(width = 0.04) +
  theme(legend.position = "none")
```

Distance p\<0.05 (sig)

```{r}
#| echo: false
#| warning: false

distance_shap <- df.overall %>%
  filter(VARIABLE %in% c("DIST_NO", "SHORT_DIST", "MEDIUM_DIST", "LONG_DIST")) %>%
  ungroup() %>%
  shapiro_test(VALUE)
  
distance_shap %>% 
  kbl(caption = "Shapiro-Wilk Test - Distance",
      col.names = c("Variable", "Statistic", "p-value")) %>%
  kable_classic_2(full_width = FALSE)

distance_plot <- df.overall %>%
    filter(VARIABLE %in% c("DIST_NO", "SHORT_DIST", "MEDIUM_DIST", "LONG_DIST"))

ggplot(distance_plot, aes(x= VARIABLE, y = VALUE)) +
  geom_violin(scale = "count", aes(fill = VARIABLE)) +
  geom_boxplot(width = 0.03) +
  theme(legend.position = "none")
```

Receiver density p\<0.05 (sig)

```{r}
#| echo: false
#| warning: false

reciever_shap <- df.overall %>%
  filter(VARIABLE %in% c("EVEN", "SUPERIOR", "INFERIOR", "LEADING", "UNCONTESTED", "SHOT_GOAL", "RECIEVE_NO")) %>%
  ungroup() %>%
  shapiro_test(VALUE)
  
reciever_shap %>% 
  kbl(caption = "Shapiro-Wilk Test - Receiever Density",
      col.names = c("Variable", "Statistic", "p-value")) %>%
  kable_classic_2(full_width = FALSE)

reciever_plot <- df.overall %>%
    filter(VARIABLE %in% c("EVEN", "SUPERIOR", "INFERIOR", "LEADING", "UNCONTESTED", "SHOT_GOAL", "RECIEVE_NO"))

ggplot(reciever_plot, aes(x= VARIABLE, y = VALUE)) +
  geom_violin(scale = "count", aes(fill = VARIABLE)) +
 # geom_boxplot(width = 0.02) +
  theme(legend.position = "none")
```

Outcome p\<0.05 (sig)

```{r}
#| echo: false
#| warning: false

result_shap <- df.overall %>%
  filter(VARIABLE %in% c("EFFECTIVE", "INEFFECTIVE", "NEUTRAL")) %>%
  ungroup() %>%
  shapiro_test(VALUE)
  
result_shap %>% 
  kbl(caption = "Shapiro-Wilk Test - Disposal Outcome",
      col.names = c("Variable", "Statistic", "p-value")) %>%
  kable_classic_2(full_width = FALSE)

result_plot <- df.overall %>%
    filter(VARIABLE %in% c("EFFECTIVE", "INEFFECTIVE", "NEUTRAL"))

ggplot(result_plot, aes(x= VARIABLE, y = VALUE)) +
  geom_violin(scale = "count", aes(fill = VARIABLE)) +
  geom_boxplot(width = 0.02) +
  theme(legend.position = "none")
```

### 
